Global phase diagram and possible quantum spin liquid in the triangular $J-K-\Gamma$ model

### 2019-12-25 paper/paper.tex
20191225 14:26

\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{color}
% \usepackage{changes}
    % \definechangesauthor[name={Wang Shi}, color=orange]{swang}

@@

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liqiud (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

@@

@@

>>>>

\documentclass[aps,prb,reprint,groupedaddress,showpacs,amsfonts,amsmath,amssymb,superscriptaddress]{revtex4-1}
\usepackage{graphicx}
% \usepackage{subfigure}
\usepackage{bm}
\usepackage{color}
% \usepackage{changes}
    % \definechangesauthor[name={Wang Shi}, color=orange]{swang}

@@

On the other hand, exchange frustation in systems with strongly anisotropic magnetic interactions has been shown to be another promising approach to explore exotic quantum spin states. Like geometric frustation, the effect of exchange frustration is to prevent the formation of long range magnetic order and given raise to a residual ground-state entropy. The spin-$1/2$ Kitaev model \cite{Kitaev2006} on honeycomb lattice, which has both gapped and gapless quantum spin liquid (QSL) ground state (GS) supporting fractionalized excitations, is an example of a model with exchange frustration. As pointed out by Jackeli and Khaliullin \cite{Khaliullin2005, PhysRevLett.102.017205}, the elementary ingredients for realizing this highly anisotropic spin model are strong relativistic spin-orbit coupling (SOC), electron interactions, and specific geometric structure: edge sharing octahedra with 90$^\circ$ TM-O-TM bond angles. Because of its theoretical importance and potential application in quantum computing, great efforts have been made to search a solid-state realization of the Kitaev model. It was first proposed to be realized in iridates $A_2$IrO$_3$ (A = Na or Li) \cite{PhysRevLett.105.027204,PhysRevLett.108.127204,Chun2015,PhysRevLett.110.076402,PhysRevB.87.220407,PhysRevLett.110.097204,PhysRevLett.108.127203,PhysRevB.92.024413,PhysRevLett.112.077204,Rau2014}, and then turned towards $\alpha$-RuCl$_3$ \cite{PhysRevB.91.180401,Banerjee2016,PhysRevB.92.235119,PhysRevB.94.161106,PhysRevB.93.214431,PhysRevLett.118.107203,PhysRevLett.118.107203,PhysRevB.96.115103} in which Ir$^{4+}$/Ru$^{3+}$ ions are arranged in a honeycomb lattice and carry effective $j_{eff}=1/2$ moments. In fact, magnetic ions located at the center of edge-shared octahedra can not only form honeycomb lattice, but also triangular lattice and the Kitaev term can naturally be generalized to this scenario \cite{PhysRevB.93.104417,PhysRevB.89.014414}. Moreover, the symmetric off-diagonal $\Gamma$ term is allowed by symmetry and is a generic feature of S=$1/2$ models with edge sharing octahedra \cite {PhysRevLett.112.077204}. Kai Li \emph{et al.,} \cite{KaiLi2015} have studied the Heisenberg-Kitaev (HK) model on triangular lattice and a global phase diagram with a mean-field level chiral spin liquid (SL) as well as four magnetically ordered phases has been obtained. However, the effect of the $\Gamma$ term on triangluar lattice has not gain as much attention as on honeycomb lattice \cite{PhysRevLett.112.077204,Rau2014,PhysRevLett.118.107203,PhysRevB.96.115103,PhysRevB.93.214431,PhysRevB.100.144422}.

@@

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig1.pdf}
    \caption{(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedral. (b) Three different direction of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation. (c) The orientation of the cubic $x$, $y$, $z$ with respect to the octahedral. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame.}
     \label{fig:ModelDefinition}
\end{figure}

@@

\begin{figure*}
    \centering
    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_a.pdf}}\\
    % \subfigure{\includegraphics[width=0.96\textwidth]{Fig2_b_f.pdf}}\\
    \includegraphics[width=0.96\textwidth]{Fig2.pdf}
    \caption{(Color online) (a) Global phase diagram of the triangular lattice J-K-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, four different stripe phases designated as Stripe-A, Stripe-B, Stripe-C and Stripe-D, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. (b) Illustration of the FM order. All spins along the same direction. (c) Illustation of the stripe order of the $x$ type. That is the spins along the x-bond direction are parallel and adjacent chains are antiparallel. There are also stripe order of the $y$ or $z$ type, which are degenerate with the $x$ type stripe order. (d) Illustration of the 120$^\circ$ N\'{e}el order. All spins are coplanar and the angles between nearest-neighbor spins are 120$^\circ$. (e) Illustration of the Dual N\'{e}el order. The magnetic unit cell include 12 lattice sites as marked by the green dashed parallelogram.}
     \label{fig:PhaseDiagram}
\end{figure*}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig3.pdf}
    \caption{(Color online) Static structure factors for different model paramters.}
     \label{fig:StructureFactors}
\end{figure}

\begin{figure}
    \includegraphics[width=0.45\textwidth]{Fig4.pdf}
    \caption{(Color online) Map of the probabilities.}
     \label{fig:StructureFactors}
\end{figure}
